# Yemi Komolafe
## Module 2 Assgn 1
### Simple Linear Regression and Correlation

# Needed Libraries
```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)
```


# create dataset from default R dataset "airquality"
```{r}
air = airquality

```

Examine data = air
```{r}
str(air)
summary(air)

```
# Visualize
```{r}
ggpairs(air)
```

# Drop missing values (NAs)
```{r}
air2 = air %>% drop_na()

```

# Use the “ggpairs” function to develop a visualization of the relationships in this dataset and to show correlation
# values for the combinations of variables
```{r}
ggpairs(air2)
```

# Then use the “ggcorr” function to develop a correlation matrix for the variables. Hint: Use “label = TRUE”
# in the “ggcorr” function to show the correlation values.
```{r}
ggcorr(air2, label = TRUE)
```
# Question 9 Plot “Temp” (x axis) versus “Ozone” (y axis) using the “ggplot” function. Choose an appropriate
# chart type. Which statement best describes the relationship between “Temp” and “Ozone”? Ans As Temp increase, Ozone 
# increases
```{r}
ggplot(air2,aes(x=Temp,y=Ozone)) + geom_point(alpha=0.5) + theme_bw()
```
# Use Tidymodels to create a linear regression model using “Temp” to predict “Ozone”. You miss wish to call
# your model fit “lm_fit”
```{r}
air3 = recipe(Temp ~ Ozone, air2) 
    

lm_model2 = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow2 = 
  workflow() %>% 
  add_model(lm_model2) %>% 
  add_recipe(air3)

lm_fit2 = fit(lm_wflow2, air2)

```


# 10 What is the slope of this regression = 0.20006 (to four decimal place = 0.2001)
```{r}
summary(lm_fit2$fit$fit$fit)
```
# Question 13 Use the code below to generate 95% confidence intervals for the coefficients. Note that you
# may need to change “lm_fit” to the name of your model fit if you used a different name.
# True/False: A 95% confidence interval for the slope coefficient does not contain zero.
# confint(lm_fit$fit$fit$fit)
```{r}
confint(lm_fit2$fit$fit$fit)
```
# Question 14: Using your linear regression model with “Temp” to predict “Ozone”, what is the predicted
# “Ozone” value when “Temp” is equal to 80 (to two decimal places)?

# How do we make predictions when we have a transformed variable in our model? Use the predict function as usual
```{r}
#Manually
60.2683  + 2.9128*80
60.2683  + 2.9128*100
 
#Using predict function
#testdata = data.frame(Temp = c(80,100))
#predict(lm_fit, new_data = testdata)
```
# Question 15 Perform appropriate model diagnostics to verify whether or not the model appears to meet the
# four linear regression model assumptions.
# True/False: There is no evidence of non-independent (autocorrelated) residuals

      
