---
output:
  word_document: default
  html_document: default
---
# PROJECT 1

# Install Libraries
```{r}
library(tidyr)
library(tidyverse)
library(GGally) #create ggcorr and ggpairs plots
library(ggcorrplot) #create an alternative to ggcorr plots
library(dplyr)
library(ggplot2)
library(ggforce)
library(patchwork)
library(gridExtra) #used for a little fancy arranging of plots
library(car) #for the VIF function
library(glmnet)
library(skimr)
library(tidymodels)
library(mice) #package for imputation
library(VIM) #visualizing missingness
library(ranger) #for random forests
library(randomForest) #also for random forests
library(vip) #variable importance
```

# Read in Data
```{r}
train = read_csv("train.csv")
 
```

#
```{r}
str(train)
summary(train)
```

#CHECK for MIssing Data
```{r}
skim(train)
```
# Delete product_code column. Use Row wise deletion
```{r}
train = train %>% drop_na()
```

# Check 
```{r}
skim(train)
```


# Delete product_code column. Use Row wise deletion
```{r}
#train = train %>% select(-product_code)
```

#Convert all character variables to factors  
```{r}
train = train %>% mutate_if(is.character,as_factor)
```



#
```{r}
str(train)
summary(train)
```


#
```{r}
train = train %>% mutate(failure  = as_factor(failure ))  %>%
    mutate(failure = fct_recode(failure, "No" = "0", "Yes" = "1" )) %>%
   mutate(product_code  = as_factor(product_code )) %>% 
  mutate(attribute_0  = as_factor(attribute_0 )) %>%
  mutate(attribute_1  = as_factor(attribute_1 )) 
str(train)
summary(train)
 
```

```{r}
train2 = train %>% dplyr::select( "failure", "attribute_0", "attribute_1", "attribute_2", "attribute_3", "measurement_0", "measurement_1", "measurement_2", "measurement_3", "measurement_4", "measurement_5", "measurement_6", "measurement_7", "measurement_8", "measurement_9", "measurement_10", "measurement_11", "measurement_12", "measurement_13", "measurement_14", "measurement_15", "measurement_16", "measurement_17")
str(train2)
summary(train2)
```

##### ABOVE - GOOD TO GO 

# Pivoting Longer: Turning variable into rows
```{r}
longer_train <- train %>% 
  pivot_longer(measurement_0:measurement_17, names_to = "measurement", values_to = "result")  
 print(longer_train)
```

# Flipping measurement and result -1
```{r}
train %>%
 pivot_longer(measurement_0:measurement_17, names_to = "measurement", values_to = "result") %>%
  ggplot(aes(x = result)) + 
  geom_bar () +
  facet_wrap (vars(measurement), ncol = 3) +
  labs(x = "Response (on a 1 to 100 scale)", y = "result")
```
#
```{r}

```



# Box Plot
```{r}
train %>%
 pivot_longer(measurement_0:measurement_17, names_to = "measurement", values_to = "result") %>%
 ggplot(aes(y = measurement, x = result)) +
  geom_boxplot() +
   labs(x = "result", y = "measurement (on a 1 to 5 scale)")
```

# Box Plot 2
```{r}
train %>%
 pivot_longer(measurement_0:measurement_17, names_to = "measurement", values_to = "result") %>%
 ggplot(aes(y = result, x = measurement)) +
  geom_boxplot() +
   labs(x = "measurement", y = "result (on a 1 to 5 scale)")
```
#
```{r}
train = train %>% mutate(failure  = as_factor(failure ))  %>%
  mutate(failure = fct_recode(failure, "No" = "0", "Yes" = "1" ))  
str(train)
summary(train)
```




#Visualization  - Factor variable using BAR CHART
```{r}
ggplot(longer_train, aes(x = failure, fill = failure)) + geom_bar() 
```
#
```{r}
table(train$failure)
```



#
```{r}
ggplot(longer_train, aes(x = measurement, fill = result )) + geom_bar()
```


```{r}
p1 = ggplot(longer_train, aes(x = attribute_0, fill = failure)) + geom_bar(position = "fill")
p2 = ggplot(longer_train, aes(x = attribute_1, fill = failure)) + geom_bar(position = "fill")
p3 = ggplot(longer_train, aes(x = attribute_2, fill = failure)) + geom_bar(position = "fill")
p4 = ggplot(longer_train, aes(x = attribute_3, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```


#
```{r}
ggplot(longer_train, aes(x = failure, fill = measurement)) + geom_bar(position = "fill")
```
#
```{r}
p1 = ggplot(longer_train, aes(x = attribute_0, fill = measurement)) + geom_bar(position = "fill")
p2 = ggplot(longer_train, aes(x = attribute_1, fill = measurement)) + geom_bar(position = "fill")
p3 = ggplot(longer_train, aes(x = attribute_2, fill = measurement)) + geom_bar(position = "fill")
p4 = ggplot(longer_train, aes(x = attribute_3, fill = measurement)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```



# Trial
```{r}
p1 = ggplot(train, aes(x = measurement_0, fill = failure)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = measurement_1, fill = failure)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = measurement_2, fill = failure)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = measurement_3, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)

```
#
```{r}
p1 = ggplot(train, aes(x = measurement_4, fill = failure)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = measurement_5, fill = failure)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = measurement_6, fill = failure)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = measurement_7, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

#
```{r}
p1 = ggplot(train, aes(x = measurement_8, fill = failure)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = measurement_9, fill = failure)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = measurement_10, fill = failure)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = measurement_11, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

#
```{r}
p1 = ggplot(train, aes(x = measurement_12, fill = failure)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = measurement_13, fill = failure)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = measurement_14, fill = failure)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = measurement_15, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

#
```{r}
p1 = ggplot(train, aes(x = measurement_16, fill = failure)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = measurement_17, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p1,p2)
```





#ggcorr
```{r}
#use "ggcorr" to create a correlation matrix with labels and correlation reported to two decimals
ggcorr(train2, label = "TRUE", label_round = 2) 

#Alternative using the "ggcorrplot" function
corr = round(cor(train2[,1:11]), 2) #Note the ,1:11 code to select the columns for inclusion
ggcorrplot(corr, hc.order = TRUE, type = "lower",
   lab = TRUE)
```


#
```{r}
ggplot(data = train) + geom_bar(mapping = aes(x = failure))  
```



# Visual Points
```{r}
p1 = ggplot(train2, aes(x=failure, y=measurement_0  )) + geom_point() + geom_smooth(method = lm, se = FALSE) + theme_bw()
p2 = ggplot(train2, aes(x=failure, y=measurement_1  )) + geom_point() + geom_smooth(method = lm, se = FALSE) + theme_bw()
p3 = ggplot(train2, aes(x=failure, y=measurement_16  )) + geom_point() + geom_smooth(method = lm, se = FALSE) + theme_bw()
p4 = ggplot(train2, aes(x=failure, y=measurement_17  )) + geom_point() + geom_smooth(method = lm, se = FALSE) + theme_bw()
grid.arrange(p1,p2,p3,p4)
```
#
```{r}
p1 = ggplot(train2,aes(x=failure,y=measurement_0)) + geom_boxplot() + geom_jitter(alpha = 0.01) + theme_bw() + 
  theme(axis.text.x = element_text(angle = 90))
p2 = ggplot(train2,aes(x=failure,y=measurement_1)) + geom_boxplot() + geom_jitter(alpha = 0.01) + theme_bw() + 
  theme(axis.text.x = element_text(angle = 90))
p3 = ggplot(train2,aes(x=failure,y=measurement_16)) + geom_boxplot() + geom_jitter(alpha = 0.01) + theme_bw() + 
  theme(axis.text.x = element_text(angle = 90))
p4 = ggplot(train2,aes(x=failure,y=measurement_17)) + geom_boxplot() + geom_jitter(alpha = 0.01) + theme_bw() + 
  theme(axis.text.x = element_text(angle = 90))
grid.arrange(p1,p2,p3,p4)
```




#
```{r}
train2 %>% count(failure)
```
#
```{r}
head(train2)
```

#Cal Mean
```{r}
mean(train2$measurement_0)
mean(train2$measurement_1)
mean(train2$measurement_2)
mean(train2$measurement_3)
mean(train2$measurement_15)
mean(train2$measurement_16)
mean(train2$measurement_17)
```

#Cal Std Deviation
```{r}
sd(train2$measurement_0)
sd(train2$measurement_1)
sd(train2$measurement_2)
sd(train2$measurement_3)
sd(train2$measurement_15)
sd(train2$measurement_16)
sd(train2$measurement_17)
```

#
```{r}
aggregate(train2$measurement_0, by = list(failure = train2$failure),mean)
aggregate(train2$measurement_1, by = list(failure = train2$failure),mean)
aggregate(train2$measurement_2, by = list(failure = train2$failure),mean)
aggregate(train2$measurement_3, by = list(failure = train2$failure),mean)
aggregate(train2$measurement_15, by = list(failure = train2$failure),mean)
aggregate(train2$measurement_16, by = list(failure = train2$failure),mean)
aggregate(train2$measurement_17, by = list(failure = train2$failure),mean)
```



# overlapping lines
```{r}
p1 = ggplot(data = train, mapping = aes(x = measurement_0, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p2 = ggplot(data = train, mapping = aes(x = measurement_1, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p3 = ggplot(data = train, mapping = aes(x = measurement_2, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p4 = ggplot(data = train, mapping = aes(x = measurement_3, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
grid.arrange(p1,p2,p3,p4)
```

#
```{r}
p1 = ggplot(data = train, mapping = aes(x = measurement_4, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p2 = ggplot(data = train, mapping = aes(x = measurement_5, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p3 = ggplot(data = train, mapping = aes(x = measurement_6, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p4 = ggplot(data = train, mapping = aes(x = measurement_7, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
grid.arrange(p1,p2,p3,p4)
```

#
```{r}
p1 = ggplot(data = train, mapping = aes(x = measurement_8, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p2 = ggplot(data = train, mapping = aes(x = measurement_9, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p3 = ggplot(data = train, mapping = aes(x = measurement_10, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p4 = ggplot(data = train, mapping = aes(x = measurement_11, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
grid.arrange(p1,p2,p3,p4)
```

#
```{r}
p1 = ggplot(data = train, mapping = aes(x = measurement_12, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p2 = ggplot(data = train, mapping = aes(x = measurement_13, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p3 = ggplot(data = train, mapping = aes(x = measurement_14, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p4 = ggplot(data = train, mapping = aes(x = measurement_15, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p5 = ggplot(data = train, mapping = aes(x = measurement_16, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
p6 = ggplot(data = train, mapping = aes(x = measurement_17, colour = failure)) +
  geom_freqpoly(binwidth = 0.1)
grid.arrange(p1,p2,p3,p4,p5,p6)
```
#Shorten variable names "measurement)
```{r}
train <- train %>% rename ("m0" = "measurement_0" , "m1" = "measurement_1" , "m2" = "measurement_2" , "m3" = "measurement_3" , 
                          "m4" = "measurement_4" , "m5" = "measurement_5" , "m6" = "measurement_6", "m7" = "measurement_7" , 
                         "m8" = "measurement_8" ,"m9" = "measurement_9",  "m10" = "measurement_10", "m11" = "measurement_11" ,
                          "m12" = "measurement_12" , "m13" = "measurement_13" , "m14" = "measurement_14" ,
                           "m15" = "measurement_15"  , "m16" = "measurement_16" , "m17" = "measurement_17")
print(train)
```

#
```{r}
train %>%
 pivot_longer(m0:m17, names_to = "measurement", values_to = "result") %>%
 ggplot(aes(y = result, x = measurement)) +
  geom_boxplot() +
   labs(x = "measurement", y = "result (on a 1 to 5 scale)")

```

 












